---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltWorkflows

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of tiltWorkflows is to make it easy to run tilt workflows.

## Installation

You can install the development version of tiltWorkflows like so:

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltWorkflows")
```

## Example

```{r message=FALSE}
library(tiltWorkflows)
```

Run [`workflows()` and
`use_workflow()`](https://2degreesinvesting.github.io/tiltWorkflows/reference/use_workflow.html)
to see available workflows and then create a workflow file into your working
directory.

```{r}
workflows()

use_workflow("profile_emissions.Rmd")
```

*Knit* the workflow file to render an example with toy data, or *Knit with
Parameters* to use your own data.

<img src=https://github.com/2DegreesInvesting/tiltWorkflows/assets/5856545/21464b5a-cd5d-4189-9f92-7978acc13c1a width=150>

Learn more about [using parameters](https://2degreesinvesting.github.io/tiltWorkflows/articles/tiltWorkflows.html).

```{r cleanup, echo=FALSE}
unlink("profile_emissions.Rmd")
```

