---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltWorkflows

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml)
[![tiltWorkflows status badge](https://2degreesinvesting.r-universe.dev/badges/tiltWorkflows)](https://2degreesinvesting.r-universe.dev/tiltWorkflows)
<!-- badges: end -->

The goal of tiltWorkflows is to make it easy to run tilt workflows.

Main features:

* Easily access toy inputs to try any workflow.
* Easily access any workflow file.
* Use your own data without writing code.
* Easily share a reproducible report on GitHub.
* Run large datasets that normally saturate your computer's memory.
* Run faster than normal by running multiple chunks of data in parallel.
* Resume after interruptions without recomputing completed chunks.

## Installation

You can install the development version from [r-universe](https://r-universe.dev/):

``` r
options(repos = c("https://2degreesinvesting.r-universe.dev", getOption("repos")))
install.packages("tiltWorkflows")
```

Or from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltWorkflows")
```

Having trouble? Try it on a fresh new project on https://posit.cloud/ (free).

## Example

```{r message=FALSE}
library(tiltWorkflows)
```

* Create a workflow file into your working directory.

```{r}
use_workflow("profile_emissions.Rmd")
```

* Create an input/ directory with toy datasets.

```{r}
use_toy_input()
```

* Render the workflow to create a report and output/ files with results.

```{r}
# Or click "Knit" in RStudio
render("profile_emissions.Rmd", quiet = TRUE)

list.files("output")
```

To learn more see [Get started](https://2degreesinvesting.github.io/tiltWorkflows/articles/tiltWorkflows.html).

```{r cleanup, echo=FALSE}
cleanup_io()
cleanup_profile_emissions()
```
