---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tiltWorkflows

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/2DegreesInvesting/tiltWorkflows/actions/workflows/R-CMD-check.yaml)
[![tiltWorkflows status badge](https://2degreesinvesting.r-universe.dev/badges/tiltWorkflows)](https://2degreesinvesting.r-universe.dev/tiltWorkflows)
<!-- badges: end -->

The goal of tiltWorkflows is to make it easy to run tilt workflows.

Main features:

* Easily access toy inputs to try any workflow.
* Easily access any workflow file.
* Use your own data without writing code.
* Easily share a reproducible report on GitHub.
* Run large datasets that normally saturate your computer's memory.
* Run faster than normal by running multiple chunks of data in parallel.
* Resume after interruptions without recomputing completed chunks.

## Installation

You can install the development version from [r-universe](https://r-universe.dev/):

``` r
options(repos = c("https://2degreesinvesting.r-universe.dev", getOption("repos")))
install.packages("tiltWorkflows")
```

Or from [GitHub](https://github.com/):

``` r
# install.packages("pak")
pak::pak("2DegreesInvesting/tiltWorkflows")
```

Having trouble? Try it on a fresh new project on https://posit.cloud/ (free).

## Example

```{r message=FALSE}
library(tiltWorkflows)
```

* `use_toy_input()` to create an input/ folder with toy datasets in your working
directory.

```{r error=TRUE}
use_toy_input()

list.files("input")

# It won't overwrite an existing input/ directory
use_toy_input()
```

* `use_workflow()` to create a workflow file into your working directory.

```{r error=TRUE}
# The error shows what's available
use_workflow()

use_workflow("profile_emissions.Rmd")
```

* To run the workflow and create a report with the results click on Knit or [Knit
with
Parameters](https://2degreesinvesting.github.io/tiltWorkflows/articles/tiltWorkflows.html).

To share a link to the output ".md" file you may run [`gh gist create
profile_emissions.md`](https://cli.github.com/manual/gh_gist) or paste its
contents into a [new GitHub gist](https://gist.github.com).

```{r cleanup, echo=FALSE}
unlink("profile_emissions.Rmd")
fs::dir_delete("input")
```
