---
title: "Run profile_emissions()"
output: github_document
params:
  chunks: 3
  input: "~/Downloads/tilt/input"
  output: "~/Downloads/tilt/output"
  emissions_profile_any_companies: "emissions_profile_any_companies.csv"
  emissions_profile_products: "emissions_profile_products.csv"
  europages_companies: "europages_companies.csv"
  ecoinvent_activities: "ecoinvent_activities.csv"
  ecoinvent_europages: "ecoinvent_europages.csv"
  isic: "isic.csv"
---


<!-- This file is generated from inst/extdata. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This workflow runs in chunks of the `*companies` data and caches intermediate
results. This saves memory, completes faster, and allows you to resume after
interruptions.

## Setup

```{r global}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(rappdirs)
library(future)
library(fs)
# Masking `tiltIndicatorAfter::profile*()` to handle larger datasets by chunks
library(tiltWorkflows)

options(
  # Split data in chunks to save memory.
  # TODO: Modify the parameter to try different numbers, e.g. 3, 30, 300 ...
  tiltWorkflows.chunks = params$chunks,
  # Read data quietly
  readr.show_col_types = FALSE,
  # Make printed output wider
  width = 500
)

# Enable computing over multiple workers in parallel
plan(multisession)
# Create a folder to save results
dir_create(params$output)
```
## Data

This example defaults to using toy datasets but you may [use the
parameters](https://2degreesinvesting.github.io/tiltWorkflows/articles/tiltWorkflows.html)
of this file to instead use your own data.

```{r}
europages_companies <- path(params$input, params$europages_companies) |>
  read_csv_falling_back_to(tiltIndicatorAfter::ep_companies) |>
  # FIXME: Move to `profile_*()`
  select(
    "company_name",
    "country",
    "company_city",
    "postcode",
    "address",
    "main_activity",
    "companies_id"
  )

ecoinvent_activities <- path(params$input, params$ecoinvent_activities) |>
  read_csv_falling_back_to(tiltIndicatorAfter::ecoinvent_activities)

ecoinvent_europages <- path(params$input, params$ecoinvent_europages) |>
  read_csv_falling_back_to(tiltIndicatorAfter::matches_mapper)

isic <- path(params$input, params$isic) |>
  read_csv_falling_back_to(tiltIndicatorAfter::isic_tilt_mapper)
```
## Emissions profile

```{r}
# Load data specific to this indicator
emissions_profile_any_companies <- path(params$input, params$emissions_profile_any_companies) |>
  read_csv_falling_back_to(read_csv(toy_emissions_profile_any_companies()))

# FIXME User toy_emissions_profile_products_ecoinvent()
# See https://github.com/2DegreesInvesting/tiltToyData/pull/12
# https://github.com/2DegreesInvesting/tiltWorkflows/issues/9
emissions_profile_products <- path(params$input, params$emissions_profile_products) |>
  read_csv_falling_back_to(read_csv(toy_emissions_profile_products()))

emissions_profile <- profile_emissions(
  companies = emissions_profile_any_companies,
  co2 = emissions_profile_products,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

emissions_profile |>
  unnest_product() |>
  write_csv(path(params$output, "emissions_profile_at_product_level.csv")) |>
  print()

emissions_profile |>
  unnest_company() |>
  write_csv(path(params$output, "emissions_profile_at_company_level.csv")) |>
  print()
```
## Results

```{r}
# NOTE: If other workflows run before this one, this shows the results of all
params$output |> dir_tree()
```

## Cleanup

Here is the cache that allows you to resume after interruptions.

```{r eval=dir_exists(user_cache_dir("tiltWorkflows"))}
# NOTE: If other workflows run before this one, this shows the cache of all
dir_tree(user_cache_dir("tiltWorkflows"))
```

If you want to recompute some result, you must first delete the relevant cache:

```r
library(fs)
library(rappdirs)

dir_delete(user_cache_dir("tiltWorkflows/PROFILE-DIRECTORY-YOU-WANT-TO-DELETE"))
```

