---
title: "Using parameters"
params: 
  output: "output"
  file: "example.csv"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Computational documents may have parameters in their header that allow you to
change the behavior of the document without changing its code.

For example, consider this header:


```{r echo=FALSE, comment=""}
this_file <- fs::path(getwd(), "tiltWorkflows.Rmd")
writeLines(head(readLines(this_file), 6))
```

Each parameter is an element of the `params` list:

```{r}
params
```

Computational documents can use those parameters in many ways, for example, to
create paths:

```{r}
file.path(params$output, params$file)
```

You can set your own parameters in RStudio. Open the document and click on "Knit
with Parameters ...":

<img src=https://github.com/2DegreesInvesting/tiltWorkflows/assets/5856545/afcbe4ee-4ce2-4e0a-a095-0644e915a922 width=150>

Change the defaults as you need then click on "Kint".

<img src=https://github.com/2DegreesInvesting/tiltWorkflows/assets/5856545/7255838b-f410-4c07-9938-2b94c15b18e3 width=500>

Learn more about [parametrized computational documents](https://docs.posit.co/connect/user/param-rmarkdown/).
