---
title: "Run all `profile*()` functions"
params:
  chunks: 3
  input: "~/Downloads/tilt/input"
  output: "~/Downloads/tilt/output"
  emissions_profile_any_companies: "emissions_profile_any_companies.csv"
  emissions_profile_products: "emissions_profile_products.csv"
  emissions_profile_upstream_products: "emissions_profile_upstream_products.csv"
  sector_profile_any_scenarios: "sector_profile_any_scenarios.csv"
  sector_profile_companies: "sector_profile_companies.csv"
  sector_profile_upstream_companies: "sector_profile_upstream_companies.csv"
  sector_profile_upstream_products: "sector_profile_upstream_products.csv"
  europages_companies: "europages_companies.csv"
  ecoinvent_activities: "ecoinvent_activities.csv"
  ecoinvent_europages: "ecoinvent_europages.csv"
  ecoinvent_inputs: "ecoinvent_inputs.csv"
  isic: "isic.csv"
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This workflow creates the output of for all `profile*()` functions in chunks of
data, to save memory and time, and using a cache to help you resume after
interruptions.

## Setup

```{r global}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(rappdirs)
library(future)
library(fs)
library(tiltWorkflows)

options(
  # Split data in chunks to save memory. 
  # TODO: Experiment with different numbers
  tiltWorkflows.chunks = params$chunks,
  # Read data quietly
  readr.show_col_types = FALSE,
  # Make printed output wider
  width = 500
)
# Enable computing over multiple workers in parallel
plan(multisession)
# Create a folder to save results
dir_create(params$output)
```

## Data

This example defaults to using toy datasets but you may [use the
parameters](https://2degreesinvesting.github.io/tiltWorkflows/articles/using-parameters.html)
of this file to instead use your own data.

```{r}
europages_companies <- path(params$input, params$europages_companies) |>
  read_csv_falling_back_to(tiltIndicatorAfter::ep_companies) |>
  # FIXME: Move to `profile_*()`
  select(
    "company_name",
    "country",
    "company_city",
    "postcode",
    "address",
    "main_activity",
    "companies_id"
  )

ecoinvent_activities <- path(params$input, params$ecoinvent_activities) |>
  read_csv_falling_back_to(tiltIndicatorAfter::ecoinvent_activities)

ecoinvent_europages <- path(params$input, params$ecoinvent_europages) |>
  read_csv_falling_back_to(tiltIndicatorAfter::matches_mapper)

ecoinvent_inputs <- path(params$input, params$ecoinvent_inputs) |>
  read_csv_falling_back_to(tiltIndicatorAfter::ecoinvent_inputs) |>
  # FIXME: Move to `profile_*()`
  select(
    "input_activity_uuid_product_uuid",
    "exchange_name",
    "exchange_unit_name"
  ) |>
  distinct()

isic <- path(params$input, params$isic) |>
  read_csv_falling_back_to(tiltIndicatorAfter::isic_tilt_mapper)
```

## Emissions profile

```{r}
# Load data specific to this indicator
emissions_profile_any_companies <- path(params$input, params$emissions_profile_any_companies) |>
  read_csv_falling_back_to(read_csv(toy_emissions_profile_any_companies()))

# FIXME User toy_emissions_profile_products_ecoinvent()
# See https://github.com/2DegreesInvesting/tiltToyData/pull/12
# https://github.com/2DegreesInvesting/tiltWorkflows/issues/9
emissions_profile_products <- path(params$input, params$emissions_profile_products) |>
  read_csv_falling_back_to(read_csv(toy_emissions_profile_products()))

emissions_profile <- profile_emissions(
  companies = emissions_profile_any_companies,
  co2 = emissions_profile_products,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

emissions_profile |>
  unnest_product() |>
  write_csv(path(params$output, "emissions_profile_at_product_level.csv")) |>
  print()

emissions_profile |>
  unnest_company() |>
  write_csv(path(params$output, "emissions_profile_at_company_level.csv")) |>
  print()
```

## Emissions profile upstream

```{r}
# Load data specific to this indicator
# FIXME User toy_emissions_profile_upstream_products_ecoinvent()
# See https://github.com/2DegreesInvesting/tiltToyData/pull/12
# https://github.com/2DegreesInvesting/tiltWorkflows/issues/9
emissions_profile_upstream_products <- path(params$input, params$emissions_profile_upstream_products) |>
  read_csv_falling_back_to(read_csv(toy_emissions_profile_upstream_products()))

# Create results at product and company level
emissions_profile_upstream <- profile_emissions_upstream(
  companies = emissions_profile_any_companies,
  co2 = emissions_profile_upstream_products,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_inputs = ecoinvent_inputs,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

emissions_profile_upstream |>
  unnest_product() |>
  write_csv(path(params$output, "emissions_profile_upstream_at_product_level.csv")) |>
  print()

emissions_profile_upstream |>
  unnest_company() |>
  write_csv(path(params$output, "emissions_profile_upstream_at_company_level.csv")) |>
  print()
```

## Sector profile

```{r}
# Load data specific to this indicator
sector_profile_companies <- path(params$input, params$sector_profile_companies) |>
  read_csv_falling_back_to(read_csv(toy_sector_profile_companies()))

sector_profile_any_scenarios <- path(params$input, params$sector_profile_any_scenarios) |>
  read_csv_falling_back_to(read_csv(toy_sector_profile_any_scenarios()))

# Create results at product and company level
sector_profile <- profile_sector(
  companies = sector_profile_companies,
  scenarios = sector_profile_any_scenarios,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

sector_profile |>
  unnest_product() |>
  write_csv(path(params$output, "sector_profile_at_product_level.csv")) |>
  print()

sector_profile |>
  unnest_company() |>
  write_csv(path(params$output, "sector_profile_at_company_level.csv")) |>
  print()
```

## Sector profile upstream

```{r}
# Load data specific to this indicator
sector_profile_upstream_companies <- path(params$input, params$sector_profile_upstream_companies) |>
  read_csv_falling_back_to(read_csv(toy_sector_profile_upstream_companies()))

sector_profile_upstream_products <- path(params$input, params$sector_profile_upstream_products) |>
  read_csv_falling_back_to(read_csv(toy_sector_profile_upstream_products()))

# Create results at product and company level
sector_profile_upstream <- profile_sector_upstream(
  companies = sector_profile_upstream_companies,
  scenarios = sector_profile_any_scenarios,
  inputs = sector_profile_upstream_products,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_inputs = ecoinvent_inputs,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

sector_profile_upstream |>
  unnest_product() |>
  write_csv(path(params$output, "sector_profile_upstream_at_product_level.csv")) |>
  print()

sector_profile_upstream |>
  unnest_company() |>
  write_csv(path(params$output, "sector_profile_upstream_at_company_level.csv")) |>
  print()
```

## Results

```{r}
params$output |> dir_tree()
```

## Cleanup

For efficiency this workflow cached intermediate results. This saves time and
allows you to resume partial runs after interruptions. But if want to recompute
your results you must first delete the cache directory.

```{r eval=dir_exists(user_cache_dir("chunks"))}
user_cache_dir("chunks") |> dir_tree()

user_cache_dir("chunks") |> dir_delete()
```
