---
title: "profile_sector_upstream.Rmd"
output: github_document
params:
  chunks: 3
  input: "input"
  output: "output"
  sector_profile_upstream_companies: "sector_profile_upstream_companies.csv"
  sector_profile_any_scenarios: "sector_profile_any_scenarios.csv"
  sector_profile_upstream_products: "sector_profile_upstream_products.csv"
  europages_companies: "europages_companies.csv"
  ecoinvent_activities: "ecoinvent_activities.csv"
  ecoinvent_inputs: "ecoinvent_inputs.csv"
  ecoinvent_europages: "ecoinvent_europages.csv"
  isic: "isic.csv"
---

<!-- This file is generated from inst/extdata. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This workflow runs in chunks of the `*companies` data and caches intermediate
results. This saves memory, completes faster, and allows you to resume after
interruptions.

## Setup

```{r global}
library(dplyr, warn.conflicts = FALSE)
library(readr, warn.conflicts = FALSE)
library(rappdirs)
library(future)
library(fs)
# Masking `tiltIndicatorAfter::profile*()` to handle larger datasets by chunks
library(tiltWorkflows)

options(
  # Split data in chunks to save memory.
  # TODO: Modify the parameter to try different numbers, e.g. 3, 30, 300 ...
  tiltWorkflows.chunks = params$chunks,
  # Read data quietly
  readr.show_col_types = FALSE,
  # Make printed output wider
  width = 500
)

# Enable computing over multiple workers in parallel
plan(multisession)

# If there is no folder for inputs, create the input/ with toy datasets
if (!dir_exists(params$input)) use_toy_input()

# Create a folder to save results
dir_create(params$output)
```

<details>

<summary>Reproducibility</summary>

```{r}
getwd()

params

try(dir_tree(params$input))

dir_tree(params$output)

sessioninfo::session_info()
```

</details>

## Data

This example defaults to using toy datasets but you may [use the
parameters](https://2degreesinvesting.github.io/tiltWorkflows/articles/tiltWorkflows.html)
of this file to instead use your own data.

```{r}
europages_companies <- path(params$input, params$europages_companies) |>
  read_csv() |>
  FIXME_issue_49()
ecoinvent_activities <- path(params$input, params$ecoinvent_activities) |>
  read_csv()
ecoinvent_europages <- path(params$input, params$ecoinvent_europages) |>
  read_csv()
isic <- path(params$input, params$isic) |>
  read_csv()
```

```{r}
ecoinvent_inputs <- path(params$input, params$ecoinvent_inputs) |>
  read_csv() |>
  # FIXME: Move to `profile_*()`
  select(
    "input_activity_uuid_product_uuid",
    "exchange_name",
    "exchange_unit_name"
  ) |>
  distinct()
```

## Sector profile upstream

```{r}
# Load data specific to this indicator
sector_profile_upstream_companies <- path(params$input, params$sector_profile_upstream_companies) |>
  read_csv()

sector_profile_any_scenarios <- path(params$input, params$sector_profile_any_scenarios) |>
  read_csv()

sector_profile_upstream_products <- path(params$input, params$sector_profile_upstream_products) |>
  read_csv()

# Create results at product and company level
sector_profile_upstream <- profile_sector_upstream(
  companies = sector_profile_upstream_companies,
  scenarios = sector_profile_any_scenarios,
  inputs = sector_profile_upstream_products,
  europages_companies = europages_companies,
  ecoinvent_activities = ecoinvent_activities,
  ecoinvent_inputs = ecoinvent_inputs,
  ecoinvent_europages = ecoinvent_europages,
  isic = isic,
  low_threshold = 1 / 3,
  high_threshold = 2 / 3
)

sector_profile_upstream |>
  unnest_product() |>
  write_csv(path(params$output, "sector_profile_upstream_at_product_level.csv")) |>
  print()

sector_profile_upstream |>
  unnest_company() |>
  write_csv(path(params$output, "sector_profile_upstream_at_company_level.csv")) |>
  print()
```
## Results

```{r}
# NOTE: If other workflows run before this one, this shows the results of all
params$output |> dir_tree()
```

## Cleanup

Here is the cache that allows you to resume after interruptions.

```{r eval=dir_exists(user_cache_dir("tiltWorkflows"))}
# NOTE: If other workflows run before this one, this shows the cache of all
dir_tree(user_cache_dir("tiltWorkflows"))
```

If you want to recompute some result, you must first delete the relevant cache:

```r
library(fs)
library(rappdirs)

dir_delete(user_cache_dir("tiltWorkflows/PROFILE-DIRECTORY-YOU-WANT-TO-DELETE"))
```

